### 2016-01-25 inputs/materials_and_methods.tex
more concise material explanation, added a reference

Samples from two autotetraploid alfalfa (\emph{Medicago sativa L.}) and one diploid rice (\emph{Oryza sativa L.}) populations were available (see Table~\ref{tab:descriptive_statistics}).\\
Alfalfa populations included elite germplasm from the Po Valley (Alfalfa-PV, \cite{annicchiarico_alfalfa_2015}) and elite germplasm adapted to Mediterranean-climate environments (Alfalfa-Med, \cite{annicchiarico_adaptation_2011}). For Alfalfa-PV, 124 parent genotypes were chosen by stratified mass selection for dry matter yield over three harvests among 4,480 densely planted genotypes grown in Lodi (northern Italy) under field conditions in 2002 and 2003. The Alfalfa-Med population comprised a sample of 154 parent genotypes derived from two cycles of free intercrossing among three outstanding populations in a multi-environment study: (i) the drought-tolerant Sardinian landrace Mamuntanas; (ii) the salt-tolerant Moroccan landrace Erfoud 1; (iii) the Australian variety SARDI 10, widely adapted across moisture-favorable and drought-prone environments. \\
The Rice dataset included 437 plants belonging to 391 accessions from the Rice Germplasm Collection maintained at CRA-Rice Research Unit (Vercelli, Italy). The sampled collection comprised accessions from the five main sub-populations of \emph{O. sativa} (274 temperate japonica, 108 tropical japonica, 28 indica, 16 aus and 11 aromatic). All accessions were purified through single seed descent, and were genotypically essentially 100\% homozygous.

>>>>

Samples from two autotetraploid alfalfa (\emph{Medicago sativa L.}) and one diploid rice (\emph{Oryza sativa L.}) populations were available (see Table~\ref{tab:descriptive_statistics}).\\
Alfalfa populations included elite germplasms from the Po Valley (Alfalfa-PV) and Mediterranean-climate environments (Alfalfa-Med). For Alfalfa-PV, 124 parent genotypes were chosen by stratified mass selection for dry matter yield over three harvests. For Alfalfa-Med, 154 parent genotypes derived from two cycles of free intercrossing among three outstanding populations in a multi-environment study. For further details see \cite{Annicchiarico2015}. \\
The Rice dataset included 437 plants belonging to 391 accessions from the Rice Germplasm Collection maintained at CRA-Rice Research Unit (Vercelli, Italy). The sampled collection comprised accessions from the five main sub-populations of \emph{O. sativa} (274 temperate japonica, 108 tropical japonica, 28 indica, 16 aus and 11 aromatic). All accessions were purified through single seed descent, and were genotypically essentially 100\% homozygous.
